---
title: "Analytical pipeline"
author: "Jerry Moxley"
date: "May 14, 2019"
output: html_document
---
## Allometry Project

> How does seed weight scale with height?
- H0 no relationship
- H1 linear, scaling slope ~ 1
- H2 Cubic, length scales to third power w/ volume (i.e., mass)
- H3 2nd power, grows in single dimension

```{r echo = F}
#read in data from online repo
seeds <- read.csv("https://raw.githubusercontent.com/jmadin/himbr/master/data/seed_root_herbivores.csv", as.is = T, text = "download")
str(seeds)
```

## A function for standard error 
```{r}
#heres a fxn for calc standard error
standard.err <- function(x){
  #this calc's standard error
  sd(x, na.rm = T) / sqrt(length(x))
}
```

## Seeds plotting, weight ~ height
```{r}
#plot(seeds$Height, seeds$Weight)
plot(Weight ~ Height, data = seeds)
```

## Data Transformation

```{r}
#add new col
seeds$Weight_log10 <- log10(seeds$Weight)
seeds$Height_log10 <- log10(seeds$Height)
plot(Weight_log10 ~ Height_log10, data = seeds, col = "red", xlab = "log10(W)", ylab="log10(H)")
```


## Data analysis
We will run a linear regression on log-transformed variables to look for scaling coefficient.  

```{r}
mod <- lm(Weight_log10 ~ Height_log10, data = seeds)
summary(mod)
#store results
write.csv(mod$coef, file = "output/mod_results.csv")

anova(mod)
```


```{r}
#predictions based on regression
h <- sort(seeds$Height_log10)
pred <- predict(mod, list(Height_log10 = h), interval = "confidence")

pdf('output/hVSw_relationship.pdf')
plot(Weight_log10 ~ Height_log10, data = seeds, col = "grey", xlab = "Height, log10")
lines(h, pred[,1], col="black", lty=2)
polygon(c(h, rev(h)), c(pred[,2], rev(pred[,3])),
          col = rgb(0,0,1,0.2), border = NA)
dev.off()
```

#Conclusion
The slope of the relationship between height and weight is `r round(mod$coef[2], 2)`



